---
title: "Knapsack Lab Report"
author: "Thi Pham and Somaya Khoda Bakhsh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Libraries
First, load `knapSack` package
```{r}
library(knapSack)
```

In performance evaluation we use`rbenchmark` library.
```{r}
library(rbenchmark)
```

## Answers

### Brute force search


_How long time does it takes to run the algorithm for n = 16 objects?_

```{r, cache = TRUE}
knapsack_objects <- knapSack:::create_knapsack(2000)
bm <- benchmark(
  knapSack:::brute_force_knapsack(knapsack_objects[1:16, ], W = 5000),
  knapSack:::brute_force_knapsack_improve(knapsack_objects[1:16, ], W = 5000),
  columns = c("replications", "elapsed", "user.self", "sys.self"),
  replications = 10
)
print(bm)
```
Thus, it takes `r bm$elapsed[1]` seconds on this machine to run the brute force algorithm with 16 objects.

####Improve brute force code

The the execution time of 10 replications of the brute force algorithm with 16 object have improves from `r bm$elapsed[1]` to `r bm$elapsed[2]`.


### Dynamic

_How much time does it takes to run the algorithm for n = 500 objects?_

```{r, cache = TRUE}
knapsack_objects <- knapSack:::create_knapsack(2000)
bm <- benchmark(
  knapSack:::knapsack_dynamic(knapsack_objects[1:500, ], W = 5000),
  knapSack:::knapsack_dynamic_improve(knapsack_objects[1:500, ], W = 5000),
  columns = c("replications", "elapsed", "user.self", "sys.self"),
  replications = 10
)
print(bm)
```

Thus, it takes `r bm$elapsed[1]` seconds on this machine to run the brute force algorithm with 500 objects.

####Improve dynamic

The the execution time of 10 replications of the dynamic algorithm with 500 objects have improved from `r bm$elapsed[1]` to `r bm$elapsed[2]`.

### Greedy

_How much time does it takes to run the algorithm for n = 1000000 objects?_

```{r, cache = TRUE}
knapsack_objects <- knapSack:::create_knapsack(1000000)
bm <- benchmark(
  knapSack:::greedy_knapsack(knapsack_objects[1:1000000, ], W = 5000),
  
  columns = c("replications", "elapsed", "user.self", "sys.self"),
  replications = 10
)
print(bm)
```

Thus, it takes `r bm$elapsed` seconds on this machine to run the brute force algorithm with 1000000 objects.


